CommonMind Consortium: DLPFC

### 2020-09-16 combined_analysis/combine_all_DLPFC.Rmd
Inital commit

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

difference networks
Number of DE genes

@@

Effect of ilr should depend on Instaition
suffix 1.
zenith for Sex with autosomes

@@

# Create list preparing for meta-analysis for SCZ
df_meta = mclapply(coefTest, function(coef){
  # Run meta-analysis
  run_meta_analysis( tab.de.lst[[coef]], "FE") %>% getGeneSymbol
}, mc.cores=6)
names(df_meta) = coefTest
```

@@

# Create list preparing for meta-analysis for SCZ
df_meta.inter_sex.disease = mclapply(coefTest, function(coef){
  # Run meta-analysis
  run_meta_analysis( tab.de.inter_sex.disease.lst[[coef]], "FE") %>% getGeneSymbol
}, mc.cores=6) 
names(df_meta.inter_sex.disease) = coefTest
```

>>>>

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/combine_all_DLPFC_cache
ml git pandoc
git pull
R

@@

difference networks

@@

Effect of ilr should depend on Instaition
suffix 1.
zenith for Sex with autosomes
check zenith squared test statistics

@@

# Create list preparing for meta-analysis for SCZ
df_meta = lapply(coefTest, function(coef){
  # Run meta-analysis
  run_meta_analysis( tab.de.lst[[coef]], "FE") %>% getGeneSymbol
})#, mc.cores=6)
names(df_meta) = coefTest
```

@@

# Create list preparing for meta-analysis for SCZ
df_meta.inter_sex.disease = lapply(coefTest, function(coef){
  # Run meta-analysis
  run_meta_analysis( tab.de.inter_sex.disease.lst[[coef]], "FE") %>% getGeneSymbol
}) 
names(df_meta.inter_sex.disease) = coefTest  
```
